Analysis: The Sound of Teaching Music 1

### 2019-10-05 script/RNotebook/dynamics.Rmd
add order analysis
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@

### [Articulation](#vel_articulation)
- Individual results
   + [All](#vel_art_ind_all)
   + [Trial by trial](#vel_art_ind_trial)

@@

@@

@@

```{r vel_dyn_all_bar, echo = FALSE}　
p_vel_dyn_all <- ggplot(data = vel_dyn_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  labs(y = "KV (1-127)", subtitle = "KV: Dynamics") + coord_cartesian(ylim = c(40, 100))
p_vel_dyn_all
```

@@

>>>>

- Order analysis (teaching/performing first?)
  + [All](#vel_dyn_order_group_all)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_acc_dyn_order_group_all)

### [Articulation](#vel_articulation)

#### KV
- Individual results
  + [All](#vel_art_ind_all)
  + [Trial by trial](#vel_art_ind_trial)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_art_order_group_all)

@@

- Order analysis (teaching/performing first?)
  + [All](#vel_acc_art_order_group_all)

@@

```{r vel_dyn_all_bar, echo = FALSE}　
p_vel_dyn_all <- ggplot(data = vel_dyn_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") + coord_cartesian(ylim = c(40, 100))
p_vel_dyn_all
```

@@

## KV-Order-Dynamics
- Investigate whether there is any order effect of the conditions.

### 1. All{#vel_dyn_order_group_all}
```{r vel_dyn_order_all, echo = all}
# For each participant
vel_dyn_order <- aggregate(Velocity~SubNr*Condition*Skill*Subcomponent*Order, data = df_vel_dyn,
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_dyn_order <- cbind(vel_dyn_order[,1:5], as.data.frame(vel_dyn_order[,6]))
# Change colnames
colnames(vel_dyn_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_dyn_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_dyn_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_dyn_order_all <- cbind(vel_dyn_order_all[,1:4], as.data.frame(vel_dyn_order_all[,5]))
# Change colnames
colnames(vel_dyn_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_dyn_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_dyn_order_all_bar, echo = FALSE}
p_vel_dyn_order_all <- ggplot(data = vel_dyn_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") + coord_cartesian(ylim = c(40, 100))
p_vel_dyn_order_all
```

##### Box plot
```{r vel_dyn_order_all_box, echo = FALSE}
p_vel_dyn_order_all_box <- ggplot(data = vel_dyn_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") 
p_vel_dyn_order_all_box
```

#### Statistics
##### Normality check
```{r normality5, echo = FALSE}
# Normality check
vel_dyn_order$Subcomponent <- factor(vel_dyn_order$Subcomponent)
vel_dyn_order_norm <- by(vel_dyn_order$Mean, list(vel_dyn_order$Condition, vel_dyn_order$Subcomponent, vel_dyn_order$Order), shapiro.test)
print(vel_dyn_order_norm)
```

##### Three-way ANOVA (ez)
```{r stats9, echo = FALSE}
vel_dyn_order_aov <- ezANOVA(
  data = df_vel_dyn
  , dv = .(Velocity)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_dyn_order_aov$ANOVA$F <- round(vel_dyn_order_aov$ANOVA$F, 4)
vel_dyn_order_aov$ANOVA$p <- round(vel_dyn_order_aov$ANOVA$p, 4)
print(vel_dyn_order_aov)
```

## KV-Diff-Order-Dynamics
- Investigate whether there is any order effect of the conditions.

### 1. All{#vel_acc_dyn_order_group_all}
```{r vel_acc_dyn_order_all, echo = all}
# For each participant
vel_acc_dyn_order <- aggregate(Acc~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF"),
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_acc_dyn_order <- cbind(vel_acc_dyn_order[,1:5], as.data.frame(vel_acc_dyn_order[,6]))
# Change colnames
colnames(vel_acc_dyn_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_acc_dyn_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_acc_dyn_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_acc_dyn_order_all <- cbind(vel_acc_dyn_order_all[,1:4], as.data.frame(vel_acc_dyn_order_all[,5]))
# Change colnames
colnames(vel_acc_dyn_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_acc_dyn_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_acc_dyn_order_all_bar, echo = FALSE}
p_vel_acc_dyn_order_all <- ggplot(data = vel_acc_dyn_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics")
p_vel_acc_dyn_order_all
```

##### Box plot
```{r vel_acc_dyn_order_all_box, echo = FALSE}
p_vel_acc_dyn_order_all_box <- ggplot(data = vel_acc_dyn_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") 
p_vel_acc_dyn_order_all_box
```

#### Statistics
##### Normality check
```{r normality6, echo = FALSE}
# Normality check
vel_acc_dyn_order$Subcomponent <- factor(vel_acc_dyn_order$Subcomponent)
vel_acc_dyn_order_norm <- by(vel_acc_dyn_order$Mean, list(vel_acc_dyn_order$Condition, vel_acc_dyn_order$Subcomponent, vel_acc_dyn_order$Order), shapiro.test)
print(vel_acc_dyn_order_norm)
```

##### Three-way ANOVA (ez)
```{r stats10, echo = FALSE}
vel_acc_dyn_order_aov <- ezANOVA(
  data = subset(df_vel_acc_dyn, df_vel_acc_dyn$Subcomponent == "FtoP" | df_vel_acc_dyn$Subcomponent == "PtoF")
  , dv = .(Acc)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_acc_dyn_order_aov$ANOVA$F <- round(vel_acc_dyn_order_aov$ANOVA$F, 4)
vel_acc_dyn_order_aov$ANOVA$p <- round(vel_acc_dyn_order_aov$ANOVA$p, 4)
print(vel_acc_dyn_order_aov)
```

## KV-Order-Articulation
- Investigate whether there is any order effect of the conditions.

### 1. All{#vel_art_order_group_all}
```{r vel_art_order_all, echo = all}
# For each participant
vel_art_order <- aggregate(Velocity~SubNr*Condition*Skill*Subcomponent*Order, data = df_vel_art,
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_art_order <- cbind(vel_art_order[,1:5], as.data.frame(vel_art_order[,6]))
# Change colnames
colnames(vel_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_art_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_art_order_all <- cbind(vel_art_order_all[,1:4], as.data.frame(vel_art_order_all[,5]))
# Change colnames
colnames(vel_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_art_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_art_order_all_bar, echo = FALSE}
p_vel_art_order_all <- ggplot(data = vel_art_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") + coord_cartesian(ylim = c(40, 100))
p_vel_art_order_all
```

##### Box plot
```{r vel_art_order_all_box, echo = FALSE}
p_vel_art_order_all_box <- ggplot(data = vel_art_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") 
p_vel_art_order_all_box
```

#### Statistics
##### Normality check
```{r normality7, echo = FALSE}
# Normality check
vel_art_order$Subcomponent <- factor(vel_art_order$Subcomponent)
vel_art_order_norm <- by(vel_art_order$Mean, list(vel_art_order$Condition, vel_art_order$Subcomponent, vel_art_order$Order), shapiro.test)
print(vel_art_order_norm)
```

##### Three-way ANOVA (ez)
```{r stats11, echo = FALSE}
vel_art_order_aov <- ezANOVA(
  data = df_vel_art
  , dv = .(Velocity)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_art_order_aov$ANOVA$F <- round(vel_art_order_aov$ANOVA$F, 4)
vel_art_order_aov$ANOVA$p <- round(vel_art_order_aov$ANOVA$p, 4)
print(vel_art_order_aov)
```

## KV-Diff-Order-Articulation
- Investigate whether there is any order effect of the conditions.

### 1. All{#vel_acc_art_order_group_all}
```{r vel_acc_art_order_all, echo = all}
# For each participant
vel_acc_art_order <- aggregate(Acc~SubNr*Condition*Skill*Subcomponent*Order, data = subset(df_vel_acc_art, df_vel_acc_art$Subcomponent == "LtoS" | df_vel_acc_art$Subcomponent == "StoL"),
                               FUN = function(x){c(N = length(x), mean = mean(x), sd = sd(x))})
vel_acc_art_order <- cbind(vel_acc_art_order[,1:5], as.data.frame(vel_acc_art_order[,6]))
# Change colnames
colnames(vel_acc_art_order) <- c("SubNr", "Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD")

# Group mean
vel_acc_art_order_all <- aggregate(Mean~Condition*Skill*Subcomponent*Order, data = vel_acc_art_order,
                         FUN = function(x){round(c(N = length(x), mean = mean(x), sd = sd(x), sem = sd(x)/sqrt(length(x))), 4)})
vel_acc_art_order_all <- cbind(vel_acc_art_order_all[,1:4], as.data.frame(vel_acc_art_order_all[,5]))
# Change colnames
colnames(vel_acc_art_order_all) <- c("Condition", "Skill", "Subcomponent", "Order", "N", "Mean", "SD", "SEM")
print(vel_acc_art_order_all)
```

### Plot
#### Bar graph
- Error bars show SEM of the mean

```{r vel_acc_art_order_all_bar, echo = FALSE}
p_vel_acc_art_order_all <- ggplot(data = vel_acc_art_order_all, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SEM, ymax = Mean + SEM),
                width = .2, position = position_dodge(.9)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics")
p_vel_acc_art_order_all
```

##### Box plot
```{r vel_acc_art_order_all_box, echo = FALSE}
p_vel_acc_art_order_all_box <- ggplot(data = vel_acc_art_order, aes(x = Subcomponent, y = Mean, fill = Condition)) +
  geom_boxplot() +
  geom_dotplot(binaxis = "y", stackdir = "center", dotsize = 1, position = position_dodge(.75)) +
  facet_wrap(Order ~ .) +
  labs(y = "KV (0-127)", subtitle = "KV: Dynamics") 
p_vel_acc_art_order_all_box
```

#### Statistics
##### Normality check
```{r normality8, echo = FALSE}
# Normality check
vel_acc_art_order$Subcomponent <- factor(vel_acc_art_order$Subcomponent)
vel_acc_art_order_norm <- by(vel_acc_art_order$Mean, list(vel_acc_art_order$Condition, vel_acc_art_order$Subcomponent, vel_acc_art_order$Order), shapiro.test)
print(vel_acc_art_order_norm)
```

##### Three-way ANOVA (ez)
```{r stats12, echo = FALSE}
vel_acc_art_order_aov <- ezANOVA(
  data = subset(df_vel_acc_art, df_vel_acc_art$Subcomponent == "LtoS" | df_vel_acc_art$Subcomponent == "StoL")
  , dv = .(Acc)
  , wid = .(SubNr)
  , between = .(Order)
  , within = .(Condition, Subcomponent)
  , type = 3
  , detailed = TRUE
)
vel_acc_art_order_aov$ANOVA$F <- round(vel_acc_art_order_aov$ANOVA$F, 4)
vel_acc_art_order_aov$ANOVA$p <- round(vel_acc_art_order_aov$ANOVA$p, 4)
print(vel_acc_art_order_aov)
```
